One-step, three-factor authentication with in-ear EEG

### 2016-12-05 paper.tex
Filling out data collection and validation sections. Reworked budget section and added group member contribution section.

% Created 2016-12-02 Fri 17:30
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Max Curran and Nick Merrill}
\date{\today}
\title{One-step, three-factor authentication with in-ear EEG}
\hypersetup{
 pdfauthor={Max Curran and Nick Merrill},
 pdftitle={One-step, three-factor authentication with in-ear EEG},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.0.50.2 (Org mode 9.0.1)}, 
 pdflang={English}}
\begin{document}

@@

In our previous work, we have proposed “one-step two-factor authentication” as a
new approach to authentication that can provide the security benefits of two-
factor authentication without incurring the hassle costs of two-step verification [1].
By employing consumer-grade EEG (electroencephalogram) sensing
technologies, we demonstrated in our 2013 passthoughts study that a user can
submit both a knowledge factor (i.e., secret thought) and an inherence factor
(i.e., brainwave signal unique to the individual) in a single step by performing a
single mental task [2]. We demonstrated the robustness of this method against
impersonation attacks, including conditions where the attacker may have learned
the target’s secret thought and/or secret task [3].

@@

We propose the use of custom-fit Ear EEG technology as the platform for
investigating the feasibility, performance, and usability of one-step three-factor
authentication. In addition to the same knowledge factor and inherence factor as
in our previous work, the user can submit in the same step the possession factor
in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in
their ear. These earpieces can serve as physical tokens in the same way as bank
ATM cards and wearable hardware tokens. Furthermore, because the earpieces
are custom-fitted to each individual, they will not be able to produce good
electrical impedances when worn by a different individual.

\section{Related Work}
\label{sec:org9b2bd46}
The use of EEG as a biometric signal for user authentication has a short history.
In 2005, Thorpe et al. motivate and outline the design of a passthoughts system,
where, rather than typing a password, users authenticate 
by thinking of a passthought [6]. Since 2002, a number of independent groups have achieved 99-
100\% authentication accuracy using multi-channel sensors placed on the scalp
[7-10]. In 2013, our group showed that 99\% authentication accuracy can also be
achieved using a consumer-grade single-channel sensor [2]. In particular, the
lack of signal diversity from multiple EEG channels can be overcome by allowing
the users to choose their own personalized passthoughts (e.g., sing their favorite
song in their head). There are two significant consequences of this result. First,
the passthoughts approach is no longer constrained by the high cost (\textasciitilde{}\$10k’s)
and low usability (gel-based electrodes; aesthetic challenges of an EEG cap) of
medical-grade multi-channel devices. Second, because users can choose and
easily change their secret mental task, this approach can support one-step two-
factor authentication [1] via the simultaneous presentation of the inherence factor
(brainwave signatures due to the unique folding structures of the cortex) and the
knowledge factor (the secret mental task).

Research in in-ear EEG is only several years old. Nonetheless, the concept has
attracted a lot of attention because of the discreetness factor of in-ear EEG over
traditional scalp-based EEG. A research team at the Imperial College London
and Aarhus University published a landmark paper in 2011 that introduced the
concept of in-ear EEG, demonstrating for the first time the feasibility of recording
brainwave signals from within the ear canal [11]. Follow-up work from the same
group demonstrated its ability to produce signal-to-noise ratios comparable to
those from conventional EEG electrode placements, robustness to common
sources of artifacts, and use in a brain-computer interface (BCI) system based on
auditory evoked potentials and visual evoked potentials [12-14]. Our 2016 study
[4] was the first to merge these two streams of work, using in-ear EEG signals for
user authentication. United Sciences is currently developing a consumer
hearable called The Aware that will measure EEG from the ear [15].
Behavioral authentication methods such as keystroke dynamics [16] and speaker
authentication [17] can be categorized as one-step two-factor authentication
schemes. In both cases, the knowledge factor (password or passphrase) and
inherence factor (typing rhythm or speaker’s voice) are employed. In contrast, the
Nymi band [18] supports one-step two-factor authentication via the inherence
factor (cardiac rhythm that is supposed to be unique to each individual) and the
possession factor (the wearing of the band on the wrist). However, as far as we
know, no one has proposed or demonstrated a one-step three-factor
authentication scheme.

@@

In our original 2013 passthoughts study [2], we used unmodified commercial off-
the-shelf EEG sensing hardware. In our 2016 Ear-EEG passthoughts study [4],
we modified the off-the-shelf hardware in order to support data collection from
within the ear canal. Once modified, the same device could be used for all
participants. In the current study, we propose to build in-ear EEG sensors that
are custom-fit to the contours of the ears and ear canals of each individual
participant. Therefore, it is necessary for us to build a separate pair of devices for
each participant. In partnership with our research collaborators at Starkey
Hearing Science, who specialize in hearing-aid technologies, we will acquire
moldings of participants’ ears, and use the molds to build custom-fit acrylic
earpieces with embedded EEG electrodes.

A key research challenge is to design and build the electrodes to produce signals
of robust quality, given the small volume of the ear cavity, the small surface
areas of the electrodes, and the limited distances between the electrodes within
the ear. We will need to experiment with the locations of the electrodes, including
the reference and ground electrodes, which may be placed on the ear lobes or
behind the ears.

We propose an update and expansion of the authentication tasks, to take
advantage of our lessons learned from previous studies on the relative strengths
of different mental tasks, with regards to authentication accuracy and usability as
reported by participants. Furthermore, given the in-ear placement of the
electrodes, and hence spatial proximity to the temporal lobes, we see a unique
opportunity to design and test novel authentication tasks based on either auditory
imagery or auditory steady-state response (ASSR). We will design a suite of
authentication tasks to include:

\begin{itemize}
\item Baseline tasks
\item Motor imagery tasks (with personal secret)
\item Visual imagery tasks (with personal secret)
\item Audio imagery tasks (with personal secret)
\item Mixed audio/visual imagery tasks (with personal secret)
\item Auditory steady-state response (ASSR) tasks (using external stimuli)
\end{itemize}

This will allow us to quantify the security and usability performances of these
tasks, both collectively as they contribute to overall authentication accuracy, as
well as comparatively against one another.
We will use OpenBCI, a open-source EEG biosensing system as our data
collection platform. This requires integrating the custom-fit Ear EEG devices with
the OpenBCI board. We will also need to extend Indra, our own data collector
software, to support the recording of OpenBCI data that is synchronized with
PsychoPy, which we use for stimuli presentation. We will recruit on the order of
7-10 participants who are willing to commit to multiple session visits, first for ear
molding, then for device impedance testing, and then for one or more data
collection sessions.

@@

We performed a very small pilot study (n=2) to better assess our projects' feasibility.
Our cursory analysis indicates that we can successfully
detect EEG signals from the ear (Section 5.1), that these signals can be used
for reliable authentication among two people (Section 5.2), and that the success
of the authenticator relies on the user's chosen secret, and not just the inherence
factor of the user's unique signal (Section 5.3).

\subsection{{\bfseries\sffamily TODO} Data collection}
\label{sec:org20a2071}
\subsection{{\bfseries\sffamily TODO} Validation}
\label{sec:org28f05cd}
\subsection{Authentication performance}
\label{sec:orgfc9b24a}

@@

\begin{table}[htbp]
\caption{Authentication accuracy for each sensor position. Left and right ears were a composite of three electrode positions along the helix, front of the ear canal, and back of the ear canal.}
\centering
\begin{tabular}{lrrrrrr}
task & Left ear &  & Right Ear &  & fp1 & \\
\hline
 & FAR & FRR & FAR & FRR & FAR & FRR\\
\hline
speech & 0 & 0 & 0 & 0 & 0 & 0\\
face & 0 & 0 & 0 & 0.002 & 0 & 0\\
breathe & 0 & 0 & 0 & 0 & 0 & 0\\
listennoise & 0 & 0 & 0 & 0 & 0 & 0\\
song (eyes open) & 0 & 0 & 0 & 0 & 0 & 0\\
song & 0 & 0 & 0 & 0 & 0 & 0\\
sequence & 0 & 0 & 0 & 0 & 0 & 0\\
listentone & 0 & 0 & 0 & 0.009 & 0 & 0\\
breathe (eyes open) & 0.039 & 0 & 0 & 0 & 0 & 0\\
sport & 0.039 & 0.036 & 0 & 0 & 0 & 0\\
\end{tabular}
\end{table}

@@

\begin{table}[htbp]
\caption{FARs for right-person, wrong-task, and p-values corresponding to confidence that these FARs were drawn from the same distribution as from the right-person-right-task trials.}
\centering
\begin{tabular}{lrrr}
Task & Right ear & Left ear & fp1\\
\hline
speech & 0.311 & 0.116 & 0\\
face & 0.355 & 0.055 & 0\\
breathe & 0 & 0.240 & 0\\
listennoise & 0.322 & 0.078 & 0\\
song\(_{\text{o}}\) & 0 & 0.166 & 0\\
song & 0 & 0.211 & 0\\
sequence & 0.433 & 0 & 0\\
listentone & 0 & 0.333 & 0\\
breathe\(_{\text{o}}\) & 0.254 & 0.129 & 0\\
sport & 0.222 & 0.135 & 0\\
\hline
\textbf{p-value} & \textbf{*0.0076} & \textbf{*0.009} & N/A\\
\end{tabular}
\end{table}

@@

\section{Schedule and Budget}
\label{sec:org7b5c0f3}
We propose a 12-month schedule with two graduate students working on the
project:

\begin{itemize}
\item Months 1-6: hardware development for custom-fit earpiece; integration with OpenBCI; testing
\item Months 1-6: software integration between OpenBCI, PsychoPy, and Indra; design of new authentication tasks and implementation in PsychoPy
\item Months 7-8: experimental data collection
\item Months 9-12: data analysis; write and submit research papers
\end{itemize}
\section{References}
\label{sec:org0b0b225}
\setlength\parindent{0pt}

>>>>

% Created 2016-12-02 Fri 17:30
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Max T. Curran and Nick Merrill}
\date{\today}
\title{One-step, three-factor authentication with in-ear EEG}
\hypersetup{
 pdfauthor={Max Curran and Nick Merrill},
 pdftitle={One-step, three-factor authentication with in-ear EEG},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.0.50.2 (Org mode 9.0.1)}, 
 pdflang={English}}
\begin{document}

@@

In previous work, “one-step two-factor authentication” has been proposed as a
new approach to authentication that can provide the security benefits of two-
factor authentication without incurring the hassle costs of two-step verification [1].
By employing consumer-grade EEG (electroencephalogram) sensing
technologies, it was demonstrated in a 2013 passthoughts study that a user can
submit both a knowledge factor (i.e., secret thought) and an inherence factor
(i.e., brainwave signal unique to the individual) in a single step by performing a
single mental task [2]. Additionally, the robustness of this method against
impersonation attacks was demonstrated, including conditions where the attacker
may have learned the target’s secret thought and/or secret task [3].

@@

We propose the use of custom-fit Ear EEG technology as the platform for
investigating the feasibility, performance, and usability of one-step three-factor
authentication. In addition to the same knowledge factor and inherence factor as
in our previous work, the user can submit in the same step the possession factor
in the form of the EEG-sensing ear-piece(s) that are custom-fitted to and worn in
their ear. These earpieces can serve as physical tokens in the same way as bank
ATM cards and wearable hardware tokens. Furthermore, because the earpieces
are custom-fitted to each individual, they will likely not be able to produce good
electrical impedances when worn by a different individual.

\section{Related Work}
\label{sec:org9b2bd46}
The use of EEG as a biometric signal for user authentication has a short history.
In 2005, Thorpe et al. motivate and outline the design of a passthoughts system,
where, rather than typing a password, users authenticate 
by thinking of a passthought [6]. Since 2002, a number of independent groups have achieved 99-
100\% authentication accuracy using multi-channel sensors placed on the scalp
[7-10]. In 2013, one group showed that 99\% authentication accuracy can also be
achieved using a consumer-grade single-channel sensor [2]. In particular, the
lack of signal diversity from multiple EEG channels can be overcome by allowing
the users to choose their own personalized passthoughts (e.g., sing their favorite
song in their head). There are two significant consequences of this result. First,
the passthoughts approach is no longer constrained by the high cost (\textasciitilde{}\$10k’s)
and low usability (gel-based electrodes; aesthetic challenges of an EEG cap) of
medical-grade multi-channel devices. Second, because users can choose and
easily change their secret mental task, this approach can support one-step two-
factor authentication [1] via the simultaneous presentation of the inherence factor
(brainwave signatures due to the unique folding structures of the cortex) and the
knowledge factor (the secret mental task).

Research in in-ear EEG is only several years old. Nonetheless, the concept has
attracted a lot of attention because of the discreetness factor of in-ear EEG over
traditional scalp-based EEG. A research team at the Imperial College London
and Aarhus University published a landmark paper in 2011 that introduced the
concept of in-ear EEG, demonstrating for the first time the feasibility of recording
brainwave signals from within the ear canal [11]. Follow-up work from the same
group demonstrated its ability to produce signal-to-noise ratios comparable to
those from conventional EEG electrode placements, robustness to common
sources of artifacts, and use in a brain-computer interface (BCI) system based on
auditory evoked potentials and visual evoked potentials [12-14]. Our own 2016 study
[4] was the first to merge these two streams of work, using in-ear EEG signals for
user authentication with a consumer-grade device. United Sciences is currently
developing a consumer hearable called The Aware that will measure EEG from the ear [15].
Behavioral authentication methods such as keystroke dynamics [16] and speaker
authentication [17] can be categorized as one-step two-factor authentication
schemes. In both cases, the knowledge factor (password or passphrase) and
inherence factor (typing rhythm or speaker’s voice) are employed. In contrast, the
Nymi band [18] supports one-step two-factor authentication via the inherence
factor (cardiac rhythm that is supposed to be unique to each individual) and the
possession factor (the wearing of the band on the wrist). However, as far as we
know, no one has proposed or demonstrated a one-step three-factor
authentication scheme.

@@

In a 2013 passthoughts study [2], unmodified commercial off-
the-shelf EEG sensing hardware was used. In our 2016 Ear-EEG passthoughts study [4],
we modified the off-the-shelf hardware in order to support data collection from
within the ear canal. Once modified, the same device could be used for all
participants. In the current study, we propose to build in-ear EEG sensors that
are custom-fit to the contours of the ears and ear canals of each individual
participant. Therefore, it is necessary for us to build a separate pair of devices for
each participant. In partnership with our research collaborators at Starkey
Hearing Science, who specialize in hearing-aid technologies, we will acquire
moldings of participants’ ears, and use the molds to build custom-fit acrylic
earpieces with embedded EEG electrodes.

A key research challenge is to design and build the electrodes to produce signals
of robust quality, given the small volume of the ear cavity, the small surface
areas of the electrodes, and the limited distances between the electrodes within
the ear. We will need to experiment with the locations of the electrodes, including
the reference and ground electrodes, which may be placed on the ear lobes or
behind the ears on the left and right mastoids.

We propose an update and expansion of the authentication tasks, to take
advantage of our lessons learned from previous studies on the relative strengths
of different mental tasks, with regards to authentication accuracy and usability as
reported by participants. Furthermore, given the in-ear placement of the
electrodes, and hence spatial proximity to the temporal lobes, we see a unique
opportunity to design and test novel authentication tasks based on either auditory
imagery or auditory steady-state response (ASSR). The ten authentication tasks and their
attributes are listed in the tables below.

\begin{table}[h]
\caption{Set of tasks proposed for authentication with descriptions.}
\centering
\begin{tabular}{p{2.7cm}p{11cm}}
\hline
\textbf{Task} & \textbf{Description} \\
\hline
Breathe & Relaxed breathing with eyes closed.\\
Breathe - Open & Relaxed breathing with eyes open.\\
Sport & Imagining attempting a sport motion of participant's choice. \\
Song & Imagining a song of participant's choice playing. \\
Song - Open & Imagining a song of participant's choice playing with eyes open. \\
Speech & Imagining a phrase of participant's choice being spoken.\\
Listen - Tone & Listening to a continuous tone.\\
Listen - ASSR & Listening to noise modulated at 40 Hz.\\
Face & Imagining a person's face of participant's choice.\\
Sequence & Imagining a person's face, a number, and a word of participant's choice on timed cues.\\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\caption{Properties of authentication tasks. Tasks are listed vertically, and various properties of the tasks are listed horizontally,
with ones and zeroes denoting whether a task does or does not have that property, respectively.}
\begin{tabular}{p{2.7cm}p{1.7cm}p{1.7cm}p{1.7cm}p{1.7cm}p{1.7cm}p{1.7cm}p{1.7cm}}
\hline
\textbf{Task} & \textbf{External Stimuli} & \textbf{Chosen Secret} & \textbf{Eyes Closed} & \textbf{Motor Imagery} & \textbf{Visual Imagery} & \textbf{Audio Imagery} \\
\hline
Breathe & 0 & 0 & 1 & 0 & 0 & 0\\
Breathe - Open & 0 & 0 & 0 & 0 & 0 & 0\\
Sport & 0 & 1 & 1 & 1 & 0 & 0\\
Song & 0 & 1 & 1 & 0 & 0 & 1\\
Song - Open & 0 & 1 & 0 & 0 & 0 & 1\\
Speech & 0 & 1 & 1 & 0 & 0 & 1\\
Listen - Tone & 1 & 0 & 1 & 0 & 0 & 0\\
Listen - ASSR & 1 & 0 & 1 & 0 & 0 & 0\\
Face & 0 & 1 & 1 & 0 & 1 & 0\\
Sequence & 1 & 0 & 0 & 0 & 1 & 0\\
\hline
\end{tabular}
\end{table}

This will allow us to quantify the security and usability performances of these
tasks, both collectively as they contribute to overall authentication accuracy, as
well as comparatively against one another.
We will use OpenBCI, a open-source EEG biosensing system as our data
collection platform. This requires integrating the custom-fit Ear EEG devices with
the OpenBCI board. We will also need to extend our own data collector
software, to support the recording of OpenBCI data that is synchronized with
PsychoPy, which we use for stimuli presentation. We will recruit on the order of
20-30 participants who are willing to commit to multiple session visits, first for ear
molding, then for device impedance testing, and then for one or more data
collection sessions.

@@

We performed a very small pilot study (n=2) to better assess our projects' feasibility,
in particular the new custom-fit ear piece hardware.
Our cursory analysis indicates that we can successfully
detect EEG signals from the ear (Section 5.1), that these signals can be used
for reliable authentication among two people (Section 5.2), and that the success
of the authenticator relies on the user's chosen secret, and not just the inherence
factor of the user's unique signal (Section 5.3).

\subsection{Data collection}
\label{sec:org20a2071}

Our initial participants were recruited from a nearby university and scheduled for ear molding
and impedance checking sessions. Finally, the data collection visit was scheduled and took
approximately 90 minutes for set up and experiment execution. The OpenBCI system we used
allows for 8 channels of simultaneous recording, along with separate ground and reference channels.
Data was initially collected with the ground placed at the center of the forehead, and using the left
mastoid as reference, though we can easily re-reference to another channel by subtracting a desired
channel (such as right mastoid). Each earpiece (shown in the image below) contain three channels each: 
one placed on the helix, and two inside the canal - one front-facing and the other back-facing. The remaining
two channels were placed on the right mastoid for later re-referencing, and at approximately Fp1 (on the 
forehead above the left eye) for validating the data collected in the ears against a scalp-based measure. 
Before beginning the experiment, the data from all channels was visualized and participants were asked to
blink and clench their jaws to confirm all channels were active and properly connected.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{2EEEG.jpg}
\caption{Pair of custom-fit earpieces with 3 embedded electrodes each located at the helix and front-facing
and back-facing within the ear canal.}
\end{figure}

During the experiment, participants were seated in a comfortable position in a quiet room facing a laptop screen on which the
instructions and stimuli were presented. Each task was completed once in sets five trials each, and then
each was completed again for another five trials. Each trial was 10 seconds in length, for a total of 10 trials and 
100 seconds of data collected per task. The instructions were read aloud to the participant by the experimenter, and
the experiment was advanced using a pointer held in the participant's lap to minimize motion artifacts in the data.  
The experimenter also recorded the participant's chosen secrets for the sport, song, face, speech, and sequence
 tasks and reminded the participant of these for the second set of trials.

\subsection{Pilot Data Validation}
\label{sec:org28f05cd}

Using the pilot data from two participants, we were able to confirm the custom-fit earpieces are able to collect EEG
data using three tests: good impedances measured for the ear electrodes, alpha-band activity attenuation when a
participant's eyes were open versus closed, and the presence of a significant ASSR signal.

The recorded impedances of the earpiece electrodes were less than 5 kOhms, a benchmark used widely in previous
ear EEG work, except one. The left helix electrode of one participant was measured at 9 kOhms, and generally the 
helix impedances for both participants were higher than their ear canal counterparts. We expected this result, given that the
helix electrode relies on quality of the the earpiece's fit outside the ear, and is not as securely and tightly placed as the
electrodes within the ear canal. Nonetheless, the data from all electrodes were tested in the remaining two data quality tests.

For the alpha-attenuation test, data from the "Breathe" task was compared with that of the "Breathe - Open" task. It is a well-
known feature of EEG data that activity in the alpha-band (approximately 8-12 Hz range) increases when the eyes are closed
compared with a similar state with eyes open. For both of our pilot participants this attenuation is clearly visible even in just
a single trial's data. To further validate, we also performed this calculation on the data collected from the Fp1 electrode and see
the effect clearly here as well. It is important to note that the left ear results are reported using the right mastoid as reference, and
the right ear results in turn using the left mastoid as reference. When using the same side mastoid for reference the effect is not 
visible, though may be if we average across many trials. This is not surprising, as the further a reference electrode is from the active
channel the less "real" signal is being subtracted from the active channel. This has important design implications for eventual 
real-world deployment of this authentication method however, as it will likely involve pieces on or around both ears to properly 
function, and not just one. The figures below show the alpha attenuation in the left and right ear channels, as well as Fp1.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{001_AlphaAtt_Fp1.jpg}
\caption{Alpha-attenuation (8-12 Hz range) in Fp1 channel, referenced at left mastoid, for comparison to ear channels. Red indicates breathing data with
eyes open, blue indicates the same task with eyes closed.}
\end{figure}

\begin{figure}[h]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{001_AlphaAtt_Left.jpg}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{001_AlphaAtt_Right.jpg}
  \end{minipage}
\caption{Alpha-attenuation (8-12 Hz range) in left and right ear canal channels, referenced at opposite mastoids respectfully. Red indicates breathing data with
eyes open, blue indicates the same task with eyes closed.}
\end{figure}

Finally, for the ASSR test we calculated power spectra for data from the "Listen - ASSR" task. The audio stimulus used for this task is modulated 
at 40 Hz, which should, in turn, produce an EEG response visible in the data at 40 Hz. Strangely, in our tests we do see an ASSR spike but it is located 
around 74 Hz instead. While this has us somewhat perplexed about our stimulus, the purpose of this test was to ensure that the response seen in the ear channels 
matched the response seen from the Fp1 recordings, which is evident comparing the figures below.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{001_ASSR_Fp1.jpg}
\caption{Power spectrum for data collected from the Fp1 channel during 40 Hz ASSR stimulus. An ASSR spike is clearly visible, though not at 40 Hz where it was expected.}
\end{figure}

\begin{figure}[h]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{001_ASSR_Left.jpg}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{001_ASSR_Right.jpg}
  \end{minipage}
\caption{Power spectra for data collected from the earpiece channels during 40 Hz ASSR stimulus. Again, the spike is clearly visible though not at 40 Hz, however it 
does match the }
\end{figure}

\subsection{Authentication performance}
\label{sec:orgfc9b24a}

@@

\begin{table}[h]
\caption{Authentication accuracy for each sensor position. Left and right ears were a composite of three electrode positions along the helix, front of the ear canal, and back of the ear canal.}
\centering
\begin{tabular}{l|rr|rr|rr}
\textbf{Task} & \textbf{Left Ear} &  & \textbf{Right Ear} &  & \textbf{Fp1} & \\
\hline
 & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR} & \textbf{FAR} & \textbf{FRR}\\
\hline
Breathe & 0 & 0 & 0 & 0 & 0 & 0\\
Breathe - Open & 0.039 & 0 & 0 & 0 & 0 & 0\\
Sport & 0.039 & 0.036 & 0 & 0 & 0 & 0\\
Song & 0 & 0 & 0 & 0 & 0 & 0\\
Song - Open & 0 & 0 & 0 & 0 & 0 & 0\\
Speech & 0 & 0 & 0 & 0 & 0 & 0\\
Listen - Tone & 0 & 0 & 0 & 0.009 & 0 & 0\\
Listen - ASSR & 0 & 0 & 0 & 0 & 0 & 0\\
Face & 0 & 0 & 0 & 0.002 & 0 & 0\\
Sequence & 0 & 0 & 0 & 0 & 0 & 0\\
\end{tabular}
\end{table}

@@

\begin{table}[h]
\caption{FARs for right-person, wrong-task, and p-values corresponding to confidence that these FARs were drawn from the same distribution as from the right-person-right-task trials.}
\centering
\begin{tabular}{lrrr}
\textbf{Task} & \textbf{Right Ear} & \textbf{Left Ear} & \textbf{Fp1}\\
\hline
Breathe & 0 & 0.240 & 0\\
Breathe - Open & 0.254 & 0.129 & 0\\
Sport & 0.222 & 0.135 & 0\\
Song & 0 & 0.211 & 0\\
Song - Open & 0 & 0.166 & 0\\
Speech & 0.311 & 0.116 & 0\\
Listen - Tone & 0 & 0.333 & 0\\
Listen - ASSR & 0.322 & 0.078 & 0\\
Face & 0.355 & 0.055 & 0\\
Sequence & 0.433 & 0 & 0\\
\hline
\textbf{p-value} & \textbf{*0.0076} & \textbf{*0.009} & N/A\\
\end{tabular}
\end{table}

@@

\section{Proposed Budget}
\label{sec:org7b5c0f3}
With two graduate students working on the project and a target sample size of 30 participants
we propose the following budget:

\begin{itemize}
\item 2x 8-Channel OpenBCI Systems: \$1,200.00 (\$600.00 each)
\item 30x Pairs of custom-fit earpieces with 3 embedded electrodes including labor cost: \$5,100.00 (\$170.00 per pair)
\item 30x Compensation for two visits per participant: \$2,400.00 (\$80.00 each)
\item 2x Graduate student support for two years: \$144,000.00 (\$72,000.00 each)
\item Travel and registration costs for conferences: \$6,000
\item \textbf{Total: \$158,700.00}
\end{itemize}

\section{Group Member Contributions}
Work for this project was approximately split evenly between the two group members. Both group members were involved in the project
ideation and literature review, preparation of initial and final presentations, and preparation of this final proposal. Individually, Max created
the experimental stimulus in PsychoPy and carried out the initial data collection of the pilot participants with some support from Nick. Max 
also ran the alpha-attenuation and ASSR data validation analyses. Along with assisting in data collection, Nick developed and ran the machine
 learning authentication analyses on our pilot data.

\section{References}
\label{sec:org0b0b225}
\setlength\parindent{0pt}
